A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-11-12 05_calibration_data.Rmd
minor changes to figure 8

```{r}
# load recurse
library(recurse)
data_recurse <- data[, list(x, y, time, TAG)]

# thin the data
data_recurse <- atl_thin_data(data = data_recurse,
                              interval = 30, id_columns = "TAG",
                              method = "resample")
```

@@

```{r}
# make a data copy
data_unproc <- copy(data)
```

```{r}
# get 4 column data
data_recurse <- data_recurse[, list(x, y, time, TAG)]

@@

### Plot residence time

```{r echo=FALSE}
fig_calib_residence <-
  ggplot()+
  geom_point(data = data_res, 
             aes(x, y),
             size = 5, shape = 2,
             alpha = 0.1)+
  geom_point(data = data_recurse,
             aes(x, y, 
                 col = res_time > 5,
                 size = res_time > 5),
             shape = 19, alpha = 0.4,
             show.legend = F)+
  geom_path(data = data_recurse,
             aes(x, y),
            col = "grey", lwd = 0.2)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_size_manual(values = c(0.5, 2))+
  ggspatial::annotation_scale(location = "br")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631)
```

@@

```{r echo=FALSE}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             col = "grey20",
             alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  scale_colour_manual(values = c("grey40", pal[3]))+
  scale_shape_manual(values = c(1, 19))+
  scale_fill_distiller(palette = "RdPu")+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank())+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

```{r echo=FALSE}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 2, col = "grey")+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = "grey20",
             lwd = 1,
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = 60 * seq(3, 18, 2),
    labels = seq(3, 18, 2)
    )+
  scale_y_continuous(
    breaks = 60 * seq(5, 20, 2),
    labels = seq(5, 20, 2)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```

>>>>

```{r}
# load recurse
library(recurse)
```

@@

```{r}
# get 4 column data
data_recurse <- data_thin[, list(x, y, time, TAG)]

@@

@@

```{r echo=FALSE}
# patch with residence points and all patches
fig_basic_residence <-
  ggplot()+
  geom_sf(data = griend)+
  geom_point(data = data_res_summary, 
             aes(x_median, y_median),
             size = 10, shape = 7,
             col = "grey20",
             alpha = 1)+
  geom_point(data = data_recurse,
            aes(x, y,
                col = res_time > 5,
                shape = res_time > 5),
            show.legend = F,
            size = 2)+
  geom_sf(data = patch_sf_data,
          fill = pal[4],
          col = pal[4],
          alpha = 0.3)+
  scale_colour_manual(values = c("grey50", pal[3]))+
  scale_shape_manual(values = c(4, 19))+
  ggspatial::annotation_scale(location = "tl")+
  ggthemes::theme_few()+
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "aliceblue"))+
  coord_sf(crs = 32631,
           expand = F,
           ylim = c(5901700, 5903150),
           xlim = c(649300, 650700))
```

@@

```{r echo=FALSE}
# make figure comparing different methods
figure_patch_duration <-
  ggplot()+
  geom_point(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             show.legend = F,
            size = 2, col = "grey")+
  geom_smooth(data = patch_summary_compare,
             aes(duration, 
                 duration_real),
             se = F,
             col = pal[4],
             method = "lm",
             show.legend = F)+
  annotate(geom = "text",
           x = 600, y = 1020,
           size = 5,
           label = "R^2 == 0.98",
           parse = T)+
  scale_x_continuous(
    breaks = 60 * seq(3, 18, 2),
    labels = seq(3, 18, 2)
    )+
  scale_y_continuous(
    breaks = 60 * seq(5, 20, 2),
    labels = seq(5, 20, 2)
  )+
  coord_cartesian(expand = T,
  #             # xlim = c(400, 1050),
  #             ylim = c(250, 1050)
  )+
  geom_abline(slope = 1, lty = 2,
              col = "black")+
  ggthemes::theme_few()+
  labs(x = "inferred duration (min)",
       y = "real duration (min)")
```
